Mental health issue linked to major crimes

### 2024-09-25 Paper/Paper.qmd
Add files via upload

---
title: "Mental health issue linked to major crime"
author: Max LI
thanks: "Code and data are available at: https://github.com/ShaotongLi-Max/STA304-Paper-1-MaxLI."
date: 2024/9/21
date-format: long
abstract: "This paper discusses the relationship between mental health issues and crime, focusing on Mental Health Act Apprehensions and major crime indicators in several Toronto police divisions. A positive linear relationship is found between the number of MHA apprehensions and reported crimes, suggesting that mental health-related interventions could help reduce crime rates while supporting affected individuals."
format: 
  pdf:
    toc: true           
    toc-title: "Table of Contents" 
    toc-depth: 2    
    number_sections: true    
bibliography: references.bib
---

@@

Mental Health Act is the law that describes what should happen when someone, in mental illness, should be treated to protect themselves and others around. The new Mental Health Act issued in 2014 set new regulations towards teenagers: "MHA Apprehensions of individuals aged 17 and under have been omitted to protect youth identity. From 2014 to 2020, these individuals comprised 6.5% (4,724 of 71,717) of all MHA Apprehensions, with individuals under 12 comprising 0.4% (320 of 71,717), and 12-17 comprising 6.1% (4,404 of 71,717) respectively. There are instances where an individual’s age group is classified as “Not Recorded”; these account for 1.3% (915 of 71,717) of all MHA Apprehensions."[@mha_toronto] Now all data of MHA Apprehensions is stored in the data set provided by Toronto police department.

According to the research provided by Public Safety Canada, of the 5 million people who came into contact with police, approximately one in five (18.8%) met the criteria for a mental or substance use disorder. One in three Canadians with a mental health disorder reported having contact with police for at least one reason studied (34.4%).[@PublicSafetyCanada] This is suggesting that there could be a positive relationship between Mental illness and crime rate.

@@

In section 7, this paper explains the limitation of the original data and the model.

@@

ggplot(clean_data, aes(y = DIVISION, x = num_mha_reports)) +
  geom_bar(stat = "identity", fill = "#4E79A7", color = "black", width = 0.7, position = position_dodge(width = 0.9)) +  
  labs(title = "Number of MHA Reports by Division",
       y = "Police Division",
       x = "MHA Reports") +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5), 
    axis.text.y = element_text(size = 10),  
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, max(clean_data$num_mha_reports) * 1.05)) +  
  geom_text(aes(label = num_mha_reports), hjust = -0.3, size = 3.5)

@@

ggplot(clean_data, aes(x = DIVISION, y = num_mha_reports, group = 1)) +
  geom_line(color = "#4E79A7", size = 1) +
  geom_point(size = 3, color = "#4E79A7") + 
  labs(title = "Number of MHA Reports by Division",
       x = "Police Division", 
       y = "MHA Reports") +    
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5), 
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),  
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, max(clean_data$num_mha_reports) * 1.05)) + 
  geom_text(aes(label = num_mha_reports), vjust = -0.5, size = 3.5)

@@

ggplot(clean_data, aes(y = DIVISION, x = num_crimes)) +
  geom_bar(stat = "identity", fill = "#E15759", color = "black", width = 0.7) +  
  labs(title = "Number of Crimes by Division",
       y = "Division",
       x = "Crime Incidents") +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),  
    axis.text.y = element_text(size = 10), 
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, max(clean_data$num_crimes) * 1.05), 
                     labels = abbreviate_number) +  
  geom_text(aes(label = abbreviate_number(num_crimes)), 
            hjust = -0.3, size = 3.5)

@@

ggplot(clean_data, aes(x = DIVISION, y = num_crimes, group = 1)) +
  geom_line(color = "#E15759", size = 1) +
  geom_point(size = 3, color = "#E15759") + 
  labs(title = "Number of Crimes by Division",
       x = "Division",  
       y = "Crime Incidents") +  
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),  
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1), 
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), 
                     limits = c(0, max(clean_data$num_crimes) * 1.05), 
                     labels = abbreviate_number) +  
  geom_text(aes(label = abbreviate_number(num_crimes)), 
            vjust = -0.5, size = 3.5)

@@

scale_factor <- max(clean_data$num_mha_reports) / max(clean_data$num_crimes)
ggplot(clean_data, aes(y = DIVISION)) +
  geom_bar(aes(x = num_mha_reports), stat = "identity", fill = "#4E79A7", color = "black", width = 0.5) +
  geom_bar(aes(x = num_crimes * scale_factor), stat = "identity", fill = "#E15759", color = "black", width = 0.5, position = position_nudge(y = -0.5)) +
  labs(title = "Comparison of MHA Reports and Crimes by Division",
       y = "Division",
       x = "MHA Reports / Crime Incidents") +
  theme_minimal(base_size = 16) + 
  theme(
    plot.title = element_text(face = "bold", size = 12, hjust = 0.5),  
    axis.text.y = element_text(size = 10),  
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_x_continuous(sec.axis = sec_axis(~./scale_factor, name = "Crime Incidents"))

@@

ggplot(clean_data, aes(x = DIVISION)) +
  geom_line(aes(y = num_mha_reports, group = 1), color = "#4E79A7", size = 1) +  
  geom_point(aes(y = num_mha_reports), size = 3, color = "#4E79A7") +
  geom_line(aes(y = num_crimes * scale_factor, group = 1), color = "#E15759", size = 1) +  
  geom_point(aes(y = num_crimes * scale_factor), size = 3, color = "#E15759") +
  labs(title = "Comparison of MHA Reports and Crimes by Division",
       x = "Division",
       y = "MHA Reports") +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 12, hjust = 0.5),  
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1), 
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_y_continuous(sec.axis = sec_axis(~./scale_factor, name = "Crime Incidents", labels = abbreviate_number))

@@

By comparing the two line plot,a positive relationship between the number of MHA reports and the number of Major Crime Indicator, the number of MHA reports seems to influence the number of crime incidents accross different police divisions. In order to make sure there are linear relationship between two factors, a linear model is made to fit in this situation based on two data:

@@

model <- lm(num_crimes ~ num_mha_reports, data = clean_data)
clean_data$predicted_crimes <- predict(model, newdata = clean_data)
ggplot(clean_data, aes(x = num_mha_reports, y = num_crimes)) +
  geom_point(color = "blue") +  
  geom_line(aes(y = predicted_crimes), color = "red") + 
  labs(title = "Number of Crimes vs. Number of MHA Reports",
       x = "Number of MHA Reports",
       y = "Number of Crimes") +
  theme_minimal()
```

The p-value for both intercept and coefficient (MHA Reports) are below the significant level of 0.05, indicating a strong evidence that the relationship between MHA Reports and major crime indicator follows this linear model.

@@

summary_table <- gt(data = final_summary_df) %>%
  tab_header(title = "Linear Model Summary") %>%
  text_transform(
    locations = cells_body(columns = vars(term)),
    fn = function(x) ifelse(x == "(Intercept)", "Intercept", x)
  ) %>%
  fmt_number(
    columns = c(estimate, p.value),  
    decimals = 3
  ) %>%
  cols_label(
    estimate = "Estimate",
    p.value = "P-value"
  ) %>%
  cols_align(align = "center", columns = vars(estimate, p.value))

@@

The result of this paper shares the insight of the research by Public Safety Canada: "In the international research for both youth and adults analyzed for this report, findings suggest that certain mental health disorders, such as substance use disorder, conduct disorder, and antisocial personality disorder were shown to have a significant correlation to offending and re-offending." The p-value of our model is 4.19\*10\^-5, which is far blow the significance level of 0.05, indicating strong correlation between the number of Mental Health Act Apprehensions and the major crime indicator.[@PublicSafetyCanada]

However, other variables like population could affect the number of both MHA reports and major crime indicator. Population is not included in Major crime indicator data and MHA Apprehensions Data. Adding population as a independent variable to the model could be a way of studying the relationship between MHA reports and major crime indicator.

This paper and its model can help the government and society better allocate resources for both mental health services and law enforcement. By understanding the correlation between mental health apprehensions and crime rates, policymakers can implement targeted interventions to address underlying issues, such as providing mental health support in high-crime areas or improving police training on handling mental health incidents. Additionally, this model can assist in predicting areas where both mental health-related incidents and crime are likely to occur, helping authorities to proactively implement prevention strategies, potentially reducing crime and improving mental health outcomes.

@@

# 7.Limitation
The limitation of this paper is split into two parts: the limitation of data and the limitation of linear model

## 7.1 Data outlier
Significant outliers presents in both MHA reports and Major Crime Indicator data, which is possibly caused by a relative small smaple population as there are only 20 police division in Toronto.

@@

ggplot(long_data, aes(x = Indicator, y = Count)) +
  geom_boxplot(outlier.colour = "black", outlier.shape = 16, outlier.size = 2, fill = NA, color = "black") +
  geom_jitter(width = 0.2, alpha = 0.5) +  
  labs(title = "Boxplot of MHA Reports and Crimes",
       x = "Indicator",
       y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 15),  
    axis.title.x = element_text(hjust = 0.5, size = 15),
    axis.title.y = element_text(hjust = 0.5, size = 15)  
  )
```

@@

## 7.2 Linear model
The linear model indeed shows significant linear relationship between the number of MHA reports and major crime indicator. However, the adjusted R-squared in this model is 0.6388, indicating that there are 36.12% of the variance left unexplained by the model. This could imply that other factors, aside from MHA reports, might be influencing crime rates.

```{r,fig.pos='H'}
#| label: Summary table
#| fig-cap: Summary table of linear model
#| echo: false
#| warning: false
#| message: false

@@

summary_table <- summary_stats %>%
  gt() %>%
  tab_header(title = "Linear Model Summary") %>%
  fmt_number(
    columns = vars(Value),
    decimals = 3
  ) %>%
  cols_label(
    Statistic = "Statistic",
    Value = "Value"
  ) %>%
  cols_align(align = "center", columns = vars(Statistic, Value))
summary_table
```

## 7.3 Model residual
The residuals in this model are quite large, leading to a complex residual pattern, which may indicate potential issues with model fit or the presence of unaccounted variability in the data.

@@

plot(model, which=1)
```

@@

# 8.Reference

>>>>

---
title: "Mental health issue linked to major crimes"
author: Max LI
thanks: "Code and data are available at: https://github.com/ShaotongLi-Max/Mental_health_issue_related_to_major_crime."
date: 2024/9/21
date-format: long
abstract: "This paper discusses the relationship between mental health issues and crime, focusing on Mental Health Act Apprehensions and major crime indicators in several Toronto police divisions. A positive linear relationship is found between the number of MHA apprehensions and reported crimes, suggesting that mental health-related interventions could help reduce crime rates while also supporting affected individuals."
format: 
  pdf:
    toc: true           
    toc-title: "Table of Contents" 
    toc-depth: 2    
    number_sections: true    
bibliography: references.bib
---

@@

Mental Health Act is a law that describes what should happen when someone with a mental illness should be treated to protect themselves and others around. The new Mental Health Act issued in 2014 set new regulations towards teenagers: "MHA Apprehensions of individuals aged 17 and under have been omitted to protect youth identity. From 2014 to 2020, these individuals comprised 6.5% (4,724 of 71,717) of all MHA Apprehensions, with individuals under 12 comprising 0.4% (320 of 71,717), and 12-17 comprising 6.1% (4,404 of 71,717) respectively. There are instances where an individual’s age group is classified as “Not Recorded”; these account for 1.3% (915 of 71,717) of all MHA Apprehensions."[@mha_toronto] Now all data of MHA Apprehensions is stored in the data set provided by Toronto police department.

According to the research provided by Public Safety Canada, of the 5 million people who came into contact with police, approximately one in five (18.8%) met the criteria for a mental or substance use disorder. One in three Canadians with a mental health disorder reported having contact with police for at least one reason studied (34.4%).[@PublicSafetyCanada] This is suggesting that there could be a positive relationship between mental illness and crime rates.

@@

In section 7, this paper explains the limitation of the original data and the model. In section 8, this paper lists the cleaned data as well as the full model summary table.

@@

ggplot(clean_data, aes(y = DIVISION, x = num_mha_reports)) +
  geom_bar(stat = "identity", fill = "#A9CCE3", color = "#A9CCE3", width = 0.7, position = position_dodge(width = 0.9)) +  
  labs(title = "Number of MHA Reports by Division",
       y = "Police Division",
       x = "MHA Reports") +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5), 
    axis.text.y = element_text(size = 10),  
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, max(clean_data$num_mha_reports) * 1.05)) +  
  geom_text(aes(label = num_mha_reports), hjust = -0.3, size = 3.5)

@@

ggplot(clean_data, aes(x = DIVISION, y = num_mha_reports, group = 1)) +
  geom_line(color = "#A9CCE3", size = 1) +
  geom_point(size = 3, color = "#A9CCE3") + 
  labs(title = "Number of MHA Reports by Division",
       x = "Police Division", 
       y = "MHA Reports") +    
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5), 
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1),  
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, max(clean_data$num_mha_reports) * 1.05)) + 
  geom_text(aes(label = num_mha_reports), vjust = -0.5, size = 3.5)

@@

ggplot(clean_data, aes(y = DIVISION, x = num_crimes)) +
  geom_bar(stat = "identity", fill = "#F1948A", color = "#F1948A", width = 0.7) +  
  labs(title = "Number of Crimes by Division",
       y = "Division",
       x = "Crime Incidents") +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),  
    axis.text.y = element_text(size = 10), 
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1)), limits = c(0, max(clean_data$num_crimes) * 1.05), 
                     labels = abbreviate_number) +  
  geom_text(aes(label = abbreviate_number(num_crimes)), 
            hjust = -0.3, size = 3.5)

@@

ggplot(clean_data, aes(x = DIVISION, y = num_crimes, group = 1)) +
  geom_line(color = "#F1948A", size = 1) +
  geom_point(size = 3, color = "#F1948A") + 
  labs(title = "Number of Crimes by Division",
       x = "Division",  
       y = "Crime Incidents") +  
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),  
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1), 
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.1)), 
                     limits = c(0, max(clean_data$num_crimes) * 1.05), 
                     labels = abbreviate_number) +  
  geom_text(aes(label = abbreviate_number(num_crimes)), 
            vjust = -0.5, size = 3.5)

@@

scale_factor <- max(clean_data$num_mha_reports) / max(clean_data$num_crimes)
ggplot(clean_data, aes(y = DIVISION)) +
  geom_bar(aes(x = num_mha_reports), stat = "identity", fill = "#A9CCE3", color = "#A9CCE3", width = 0.5) +
  geom_bar(aes(x = num_crimes * scale_factor), stat = "identity", fill = "#F1948A", color = "#F1948A", width = 0.5, position = position_nudge(y = -0.5)) +
  labs(title = "Comparison of MHA Reports and Crimes by Division",
       y = "Division",
       x = "MHA Reports / Crime Incidents") +
  theme_minimal(base_size = 16) + 
  theme(
    plot.title = element_text(face = "bold", size = 12, hjust = 0.5),  
    axis.text.y = element_text(size = 10),  
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_x_continuous(sec.axis = sec_axis(~./scale_factor, name = "Crime Incidents"))

@@

ggplot(clean_data, aes(x = DIVISION)) +
  geom_line(aes(y = num_mha_reports, group = 1), color = "#A9CCE3", size = 1) +  
  geom_point(aes(y = num_mha_reports), size = 3, color = "#A9CCE3") +
  geom_line(aes(y = num_crimes * scale_factor, group = 1), color = "#F1948A", size = 1) +  
  geom_point(aes(y = num_crimes * scale_factor), size = 3, color = "#F1948A") +
  labs(title = "Comparison of MHA Reports and Crimes by Division",
       x = "Division",
       y = "MHA Reports") +
  theme_minimal(base_size = 14) + 
  theme(
    plot.title = element_text(face = "bold", size = 12, hjust = 0.5),  
    axis.text.x = element_text(size = 10, angle = 45, hjust = 1), 
    axis.title.y = element_text(face = "bold", size = 12),
    axis.title.x = element_text(face = "bold", size = 12)
  ) +
  scale_y_continuous(sec.axis = sec_axis(~./scale_factor, name = "Crime Incidents", labels = abbreviate_number))

@@

By comparing the two line plots,a positive relationship between the number of MHA reports and the number of Major Crime Indicator, the number of MHA reports seems to influence the number of crime incidents accross different police divisions. In order to confirm there are linear relationship between two factors, a linear model is made to fit in this situation based on two data:

@@

model <- lm(num_crimes ~ num_mha_reports, data = clean_data)
clean_data$predicted_crimes <- predict(model, newdata = clean_data)
ggplot(clean_data, aes(x = num_mha_reports, y = num_crimes)) +
  geom_point(color = "#A9CCE3") +  
  geom_line(aes(y = predicted_crimes), color = "#F1948A") + 
  labs(title = "Number of Crimes vs. Number of MHA Reports",
       x = "Number of MHA Reports",
       y = "Number of Crimes") +
  theme_minimal()
```

The p-values for both intercept and coefficient (MHA Reports) are below the significant level of 0.05, indicating a strong evidence that the relationship between MHA Reports and major crime indicator follows this linear model.

@@

summary_table <- gt(data = final_summary_df) %>%
  tab_header(title = "Linear Model Summary 1") %>%
  text_transform(
    locations = cells_body(columns = vars(term)),
    fn = function(x) ifelse(x == "(Intercept)", "Intercept", x)
  ) %>%
  fmt_number(
    columns = c(estimate, p.value),  
    decimals = 3
  ) %>%
  cols_label(
    estimate = "Estimate",
    p.value = "P-value"
  ) %>%
  cols_align(align = "center", columns = vars(estimate, p.value))

@@

The result of this paper shares the insight of the research by Public Safety Canada: "In the international research for both youth and adults analyzed for this report, findings suggest that certain mental health disorders, such as substance use disorder, conduct disorder, and antisocial personality disorder were shown to have a significant correlation to offending and re-offending." The p-value of our model is 4.19\*10\^-5, which is far below the significance level of 0.05, indicating a strong correlation between the number of Mental Health Act Apprehensions and the major crime indicator.[@PublicSafetyCanada]

However, other variables like population could affect the number of both MHA reports and major crime indicator. Population is not included in Major crime indicator data and MHA Apprehensions Data. Adding population as an independent variable to the model could be a way of studying the relationship between MHA reports and major crime indicator.

This paper and its model can assist the government and society better allocate resources for both mental health services and law enforcement. By understanding the correlation between mental health apprehensions and crime rates, policymakers can implement targeted interventions to address underlying issues, such as providing mental health support in high-crime areas or improving police training on handling mental health incidents. Additionally, this model can assist in predicting areas where both mental health-related incidents and crime are likely to occur, helping authorities proactively implement prevention strategies, which could potentially reducing crime and improving mental health outcomes.

@@

# 7.Limitation

The limitation of this paper is split into two parts: the limitation of data (7.1) and the limitation of linear model (7.2 & 7.3)

## 7.1 Data outlier

Significant outliers are evident in both the Mental Health Act (MHA) reports and the Major Crime Indicator data. These outliers may be attributable to the relatively small sample size, given that there are only 20 police divisions in Toronto. The limited number of divisions can lead to greater variability in the data, making it more susceptible to the influence of atypical observations.

@@

ggplot(long_data, aes(x = Indicator, y = Count)) +
  geom_boxplot(outlier.colour = "#F1948A", outlier.shape = 16, outlier.size = 2, fill = NA, color = "#A9CCE3") +
  geom_jitter(width = 0.2, alpha = 0.5, color = "#F1948A") +  
  labs(title = "Boxplot of MHA Reports and Crimes",
       x = "Indicator",
       y = "Count") +
  theme_minimal(base_size = 15) +
  theme(
    plot.title = element_text(hjust = 0.5, size = 15),  
    axis.title.x = element_text(hjust = 0.5, size = 15),
    axis.title.y = element_text(hjust = 0.5, size = 15)  
  )
```

@@

## 7.2 Model accuracy

The linear model reveals a significant linear relationship between the number of Mental Health Act (MHA) reports and the major crime indicator. However, the adjusted R-squared value of 0.6388 indicates that approximately 36.12% of the variance in crime rates remains unexplained by the model. This finding implies that, in addition to MHA reports, there are likely other influencing factors contributing to variations in crime rates.

```{r,fig.pos='H'}
#| label: Summary table
#| echo: false
#| warning: false
#| message: false

@@

summary_table <- summary_stats %>%
  gt() %>%
  tab_header(title = "Linear Model Summary 2") %>%
  fmt_number(
    columns = vars(Value),
    decimals = 3
  ) %>%
  cols_label(
    Statistic = "Statistic",
    Value = "Value"
  ) %>%
  cols_align(align = "center", columns = vars(Statistic, Value))
summary_table
```

## 7.3 Model residual

The residuals in this model are relatively large, leading to a complex residual pattern. This complexity may indicate potential issues with model fit or the presence of unaccounted variability in the data.

@@

fitted_values <- fitted(model)
residuals <- resid(model)

ggplot(data = NULL, aes(x = fitted_values, y = residuals)) +
  geom_point(color = "#A9CCE3") +     # Set point color to #A9CCE3
  geom_smooth(method = "loess", color = "#F1948A", se = FALSE) +  # Smoothed line following residuals
  labs(x = "Fitted Values", y = "Residuals") +  # Add axis labels
  theme_minimal()

@@

# 8.Appendix

```{=tex}
\begin{table}[H]
    \centering
    \caption{Linear Model Summary 3}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Statistic} & \textbf{Value} \\ \hline
        Minimum & -10046.5 \\ \hline
        1st Quartile (1Q) & -3273.8 \\ \hline
        Median & -423.9 \\ \hline
        3rd Quartile (3Q) & 4260.7 \\ \hline
        Maximum & 6344.1 \\ \hline
        \textbf{Coefficients} &  \\ \hline
        (Intercept) & 6748.2438 \\ \hline
        Std. Error (Intercept) & 2970.8029 \\ \hline
        t value (Intercept) & 2.272 \\ \hline
        Pr(>|t|) (Intercept) & 0.0373 * \\ \hline
        num\_mha\_reports & 2.4509 \\ \hline
        Std. Error (num\_mha\_reports) & 0.4397 \\ \hline
        t value (num\_mha\_reports) & 5.574 \\ \hline
        Pr(>|t|) (num\_mha\_reports) & 4.19e-05 *** \\ \hline
        \textbf{Significance Codes} & 0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1 \\ \hline
        \textbf{Residual Standard Error} & 4835 on 16 degrees of freedom \\ \hline
        \textbf{Multiple R-squared} & 0.6601 \\ \hline
        \textbf{Adjusted R-squared} & 0.6388 \\ \hline
        \textbf{F-statistic} & 31.07 on 1 and 16 DF \\ \hline
        \textbf{p-value of F-statistic} & 4.194e-05 \\ \hline
    \end{tabular}
\end{table}
```

```{=tex}
\begin{table}[H]
    \centering
    \caption{Cleaned Data}
    \begin{tabular}{|l|r|r|}
        \hline
        \textbf{Division} & \textbf{Number of Crimes} & \textbf{Number of MHA Reports} \\ \hline
        D11 & 15894 & 5435 \\ \hline
        D12 & 17151 & 5137 \\ \hline
        D13 & 14180 & 4226 \\ \hline
        D14 & 27590 & 12603 \\ \hline
        D22 & 26578 & 6302 \\ \hline
        D23 & 25782 & 5769 \\ \hline
        D31 & 29099 & 6531 \\ \hline
        D32 & 31273 & 7528 \\ \hline
        D33 & 17836 & 5516 \\ \hline
        D41 & 27591 & 6752 \\ \hline
        D42 & 24037 & 5357 \\ \hline
        D43 & 27509 & 7069 \\ \hline
        D51 & 32666 & 10233 \\ \hline
        D52 & 23487 & 5916 \\ \hline
        D53 & 21199 & 6584 \\ \hline
        D54 & 6347 & 1965 \\ \hline
        D55 & 24524 & 8636 \\ \hline
        NSA & 3992 & 755 \\ \hline
    \end{tabular}
\end{table}
```

\vspace{2em}
\newpage

# 9.Reference
